---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hello.world

<!-- badges: start -->
[![R-CMD-check](https://github.com/2DegreesInvesting/hello.world/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/2DegreesInvesting/hello.world/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of hello.world is to prove you can install and use an R package from us:

* Your version of R is new enough to work with our packages.
* You can access a CRAN, which distributes the dependencies of our packages.
* You can access at least one of the platforms where we release our packages.
* You can understand our standard instructions to install and use our packages.

## Installation

You can install the development version from
[r-universe](https://r-universe.dev/):

``` r
options(repos = c("https://2degreesinvesting.r-universe.dev", getOption("repos")))
install.packages("hello.world")
```

Or from [GitHub](https://github.com/):

``` r
# install.packages("pak")
pak::pak("2DegreesInvesting/hello.world")
```

Having trouble? Try it on a fresh new project on <https://posit.cloud/>
(free).

## Example

```{r example}
library(hello.world)

hello_world()
```
