---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tiltRequirements

<!-- badges: start -->
[![R-CMD-check](https://github.com/2DegreesInvesting/tiltRequirements/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/2DegreesInvesting/tiltRequirements/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of tiltRequirements is help you install and use R packages from
[tilt](https://www.tiltsmes.org/). It provides basic documentation and software
to prove the following:

* Your version of R is new enough to work with our packages.
* You can install the dependencies of our packages from a
[CRAN](http://cran.r-project.org/)-like repository.
* You can access at least one of the platforms where we release our packages.
* You can understand our standard instructions to install and use our packages.

## Installation

You can install the development version from
[r-universe](https://r-universe.dev/):

``` r
# install.packages("pak")
pak::repo_add(r_universe = "https://2degreesinvesting.r-universe.dev")
install.packages("tiltRequirements")
```

Or from [GitHub](https://github.com/):

``` r
# install.packages("pak")
pak::pak("2DegreesInvesting/tiltRequirements")
```

Having trouble? Try it on a fresh new project on <https://posit.cloud/>
(free).

## Example

```{r example, error=TRUE}
library(tiltRequirements)

hello()

hello("tilt")

# Errors
hello("invalid")
```

You can achieve the same with a browser-based, interactive app. You can 3 options:

1. [Online](https://tiltsmes.shinyapps.io/tiltrequirements/).
2. Offline from the R console with `hello_addin()`.
3. Offline from RStudio by searching for "hello" under Addins:


<img src=FIXME width=200>

You can also run the app online here.
