---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tiltRequirements

<!-- badges: start -->
[![R-CMD-check](https://github.com/2DegreesInvesting/tiltRequirements/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/2DegreesInvesting/tiltRequirements/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of tiltRequirements is to help you install and use R packages from
[tilt](https://www.tiltsmes.org/). It provides basic documentation and software
to prove the following:

* Your version of [R is new
enough](https://github.com/search?q=repo%3A2DegreesInvesting%2FtiltRequirements++path%3ADESCRIPTION+%22R+%28%3E%22&type=code)
to work with our packages.
* You can install the dependencies of our packages
([example](https://github.com/search?q=repo%3A2DegreesInvesting%2FtiltRequirements++path%3ADESCRIPTION+%22Imports%3A%22&type=code))
from [CRAN](http://cran.r-project.org/) or similar.
* You can access our packages from [r-universe](https://r-universe.dev/) or
[GitHub](https://github.com/).
* You understand our standard [Installation] instructions and [Examples].
* You can interact with our code from our standard [interactive
apps](https://tiltsmes.shinyapps.io/tiltrequirementsapp/).

## Installation

You can install the development version from
[r-universe](https://r-universe.dev/):

``` r
# install.packages("pak")
pak::repo_add(r_universe = "https://2degreesinvesting.r-universe.dev")
install.packages("tiltRequirements")
```

Or from [GitHub](https://github.com/):

``` r
# install.packages("pak")
pak::pak("2DegreesInvesting/tiltRequirements")
```

Having trouble? Try it on a fresh new project on <https://posit.cloud/>
(free).

## Example

```{r example, error=TRUE}
library(tiltRequirements)

hello()

hello("tilt")

# Errors
hello("invalid")
```

You can also achieve the same with an [interactive app
online](https://tiltsmes.shinyapps.io/tiltrequirementsapp/).
