---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tiltRequirements

<!-- badges: start -->
[![tiltRequirements status badge](https://2degreesinvesting.r-universe.dev/badges/tiltRequirements)](https://2degreesinvesting.r-universe.dev/tiltRequirements)
[![R-CMD-check](https://github.com/2DegreesInvesting/tiltRequirements/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/2DegreesInvesting/tiltRequirements/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/2DegreesInvesting/tiltRequirements/branch/main/graph/badge.svg)](https://app.codecov.io/gh/2DegreesInvesting/tiltRequirements?branch=main)

<!-- badges: end -->

The goal of tiltRequirements is to help you install and use R packages from
[tilt](https://www.tiltsmes.org/). It provides basic documentation and software
to prove the following:

* Your version of [R is new
enough](https://github.com/search?q=repo%3A2DegreesInvesting%2FtiltRequirements++path%3ADESCRIPTION+%22R+%28%3E%22&type=code)
to work with our packages.
* You can install from [CRAN](https://cran.r-project.org/) the dependencies that
our packages
[import](https://github.com/search?q=repo%3A2DegreesInvesting%2FtiltRequirements++path%3ADESCRIPTION+%22Imports%3A%22&type=code).
* You can access our packages from [r-universe](https://r-universe.dev/) or
[GitHub](https://github.com/).
* You understand our standard [Installation] instructions and [Example].
* You can interact with our code from our standard [interactive
apps](https://tiltsmes.shinyapps.io/tiltrequirementsapp/).

## Installation

You can install the latest release from [r-universe](https://r-universe.dev/)
with:

``` r
install.packages("tiltRequirements", repos = c("https://2degreesinvesting.r-universe.dev", getOption("repos")))
```

Or the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("2DegreesInvesting/tiltRequirements")
```

If you install from GitHub you may need to [prepare your system to build
packages from
source](https://usethis.r-lib.org/articles/usethis-setup.html#prepare-your-system-to-build-packages-from-source)
(if on Windows see "Install Rtools").

Having trouble? Try it on a fresh new project on <https://posit.cloud/>
(free).

## Example

```{r example, error=TRUE}
library(tiltRequirements)

hello()

hello("tilt")

# Errors
hello("invalid")
```

You can also achieve the same with an [interactive app
online](https://tiltsmes.shinyapps.io/tiltrequirementsapp/).

[Get started](https://2degreesinvesting.github.io/tiltRequirements/articles/tiltRequirements.html).
